\documentclass[8pt]{extarticle}
\pagestyle{empty}
\usepackage{geometry}
\geometry{
	paper=a4paper,
	top=0.75cm,
	bottom=0.5cm,
	left=.8cm,
	right=.8cm,
}

\usepackage{suffix}
\usepackage{xifthen}

\usepackage[sfdefault]{FiraSans}
\usepackage[T1]{fontenc}
\usepackage[hidelinks, pdftex, pdftitle={Curriculum Vitae – Maurice Frank}, pdfauthor={Maurice Frank}]{hyperref}
\usepackage{fontawesome}
\usepackage{xparse}
\usepackage{csquotes}

\usepackage[style=publist]{biblatex}
\plauthorname[Maurice]{Frank}
\addbibresource{pubs.bib}

\usepackage{enumitem}
\setlist{left=4pt, topsep=5pt, partopsep=0pt, parsep=0pt, itemsep=4pt}

\usepackage{multicol}
\setlength\columnsep{.8cm}

\setlength{\parindent}{0mm}
\renewcommand{\baselinestretch}{1.1}
\frenchspacing

\usepackage{tikz}
\definecolor{primary}{rgb}{0.455, 0.635, 0.365}


% Command to vertically centre adjacent content
\newcommand{\vcenteredhbox}[1]{% The only parameter is for the content to centre
	\begingroup%
		\setbox0=\hbox{#1}\parbox{\wd0}{\box0}%
	\endgroup%
}

\newcommand{\icon}[3]{% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	\vcenteredhbox{\colorbox{primary}{\makebox(#2, #2){\textcolor{white}{\LARGE\csname fa#1\endcsname}}}}% Icon and box
	\hspace{0.2cm}% Whitespace
	\vcenteredhbox{\large\textcolor{primary}{#3}}% Text
}

\newcommand{\bicon}[2]{
    \textbf{%
    \vcenteredhbox{\makebox(11, 11){\small\csname fa#1\endcsname}}%
    \hspace{0.05cm}%
    \vcenteredhbox{#2}}%
}

\newcommand*{\cvsect}[1]{
    \colorbox{primary}{\textcolor{white}{\MakeUppercase{\textbf{\large #1}}}}%
    \vspace{0.2\baselineskip}\\%
}

\WithSuffix\newcommand\cvsect*[1]{\cvsect{#1}\vspace{-0.8\baselineskip}}

\newcommand{\entry}[5]{%
    \filbreak%
    {\large #2}\vspace{0.15\baselineskip}\\%
    \bicon{MapMarker}{#3}\hfill%
    \bicon{Calendar}{#1}\vspace{.5\baselineskip}\\%
    #4\vspace{.5\baselineskip}\\%
    \ifthenelse{\isempty{#5}}{}{{\texttt{#5}}\vspace{0pt}\\}%
}%

\renewcommand{\|}{\hspace{1.2mm}/\hspace{1.2mm}}

\begin{document}
\begin{minipage}[t]{0.45\textwidth}
    \vspace{-5pt}%
    {\Huge Maurice Frank}\\

    {\Huge\textcolor{gray}{Machine learning researcher}}
\end{minipage}
\begin{minipage}[t]{.275\textwidth}
        \icon{MapMarker}{12}{Amsterdam, NL}\\
        \icon{Phone}{12}{\href{tel:0031638493722}{+31 6 38493722}}\\
        \icon{At}{12}{\href{mailto:hello@morris-frank.dev}{hello@morris-frank.dev}}\\
\end{minipage}
\begin{minipage}[t]{.275\textwidth}
	\icon{User}{12}{\href{https://morris-frank.dev}{morris-frank.dev}}\\
    \icon{Github}{12}{\href{https://github.com/morris-frank}{github.com/morris-frank}}\\
    \icon{Linkedin}{12}{\href{https://linkedin.com/in/morris-frank}{linkedin.com/in/morris-frank}}\\
\end{minipage}
\vspace{-6pt}

\begin{multicols*}{2}
% \raggedcolumns%
I like to hunt creative solutions to challenging problems with the use of machine learning.
I want my work to have a real positive impact on the world and I favour team-work with enthusiastic colleagues.
My current academic interest lies in deep generative modelling and Bayesian methods, VAEs and Flows as well as a better understanding of our deep learning methods and how to make them reliable and fair.
I am especially intrigued by work on and applications to music and sound as well as an understanding of human perception.
I have strong theoretical backgrounds on machine learning and a background in physics and mathematics.\\\\

\cvsect{Education}
\entry{2018 -- 2020}
{M.Sc. Artificial Intelligence\hfill\textit{\textbf{\normalsize awarded cum laude}}\ \textit{\normalsize GPA 4/4}}
{\href{https://uva.nl}{Universiteit van Amsterdam}}
{
    Research degree with most contemporary topics in AI/ML
    \begin{itemize}%
        \item Theory and practical implementation of the concepts of machine and deep learning: CNNs, RNNs/LSTMs, VAEs/Flows, GANs, MCMC/sampling, Gaussian process/Bayesian modelling, ICA
        \item Specialization in topics: Theoretical machine learning, Computer Vision, Reinforcement Learning, NLP, Information theory
    \end{itemize}
    \textbf{Thesis:} Investigating Bayesian methods for unsupervised music source separation. Do generative models know what they don't know? \href{https://raw.githubusercontent.com/morris-frank/thesis-tex/master/main.pdf}{\bicon{Link}{Read}}\\
    \emph{Supervisor:} \href{https://scholar.google.com/citations?user=KNJIRGkAAAAJ}{Maximilian Ilse (AMLab)}, \href{https://www.egavves.com/}{Dr Efstratios Gavves}
}
{}

\entry{2014 -- 2017}
{B.Sc. Applied Computer Science\hfill\textit{\normalsize GPA 3.58/4}}
{\href{https://uni-heidelberg.de/en}{University Heidelberg}}
{
    General degree on all topics of Computer Science
    \begin{itemize}
        \item Specialization on image processing and pattern recognition: Deep Learning, 3D Computer vision, medical image analysis, fairness in AI
        \item Courses on Practical CS, Algorithms, DBMS, Theoretical informatics, Numerical methods and software engineering
    \end{itemize}
    \textbf{Thesis:} Using a FCN-ResNet based detector the thesis provides a reverse image search tool here in particular to retrieve art historic images containing an object given by a reference image.\href{https://github.com/morris-frank/ba_latex/blob/master/thesis.pdf}{\bicon{Link}{Read}}\\
    \emph{Supervisor:} \href{https://scholar.google.com/citations?user=ZrRs-qoAAAAJ}{Dr\ Miguel Bautista Martin}, \href{https://hci.iwr.uni-heidelberg.de/Staff/bommer}{Prof.\ Dr\ Björn Ommer}
}
{}

\entry{2013 -- 2014}
{B.Sc. Physics}
{\href{https://uni-heidelberg.de/en}{University Heidelberg}}
{Change of degree after the first year, kept as minor studies.}
{}

\cvsect{Publications}%
\begin{refsection}[pubs]%
    \nocite{*}%
    \vspace{-2\topsep}%
    \printbibliography[heading=none]
    \vspace{\topsep}
\end{refsection}

\cvsect{Voluntary work}
\entry%
{11/2020 --}
{CO-Founder / Member}
{\href{http://ackersyndikat.org}{Ackersyndikat}}
{
    Germany-wide non-profit cooperative trying to build a financing model for self-organized ecological farming businesses.
}
{}

\entry%
{06/2015 --}
{CO-Founder / Member}
{\href{https://collegiumacademicum.de}{Collegium Academicum, Heidelberg}}
{
    Student-founded non-profit company building sustainable student housing.
    We are building an innovative living space for 200 young people.
    Creating an educational center for holistic self-learning.
}
{team building{\|}lead generation{\|}design work}

\columnbreak%
\cvsect{Industry experience}
\entry%
{11/2020 --}
{Machine learning scientist}
{\href{https://hummingbird-diagnostics.com/}{Hummingbird Diagnostics}, Heidelberg}
{
    Development of deep learning based approaches to cancer and disease detection from liquid biopsy (blood samples).
    Working with sequence embedding models and graph networks on microRNA biomarkers.
    Focus on unsupervised representation learning and explainability.
}
{Python{\|}PyTorch{\|}R{\|}Biostatistics}

\entry%
{06/2019 -- 08/2019}
{Machine learning engineer -- Intern}
{\href{https://bmwgroup.com}{BMW Group, Munich}}
{
    Worked within the engine development department.
    Building statistical models to analyze engine part quality and live fleet monitoring.
    Building a production-ready data visualization app.\\

    Official corporate testimony: \textit{Significantly exceeds requirements at all times} in all criteria, engineering, analytical skills and teamwork.
}
{Python{\|}PySpark{\|}Palantir Foundry{\|}Dash{\|}Agile development}

\entry%
{01/2018 -- 08/2018}
{Full-stack web developer}
{\href{https://buergerwerke.de/}{Bürgerwerke eG, Heidelberg}}
{
    Ground-up development of a team communication and organization web portal in Ruby on Rails.
    Backend and Frontend work.
    Software engineering from planning the project until complete delivery.
}
{Rails{\|}Ruby{\|}Software Engineering}

\entry%
{06/2016 -- 06/2017}
{Laboratory software administrator}
{\href{https://uni-heidelberg.de/fakultaeten/wiso/awi/index_en.html}{Alfred-Weber-Institute, Heidelberg}}
{
    Administrator in a computer lab for Behavioral Economics experiments.
    Development new features of an experiment administration software.
}
{Ruby{\|}Python{\|}Windows server}

\cvsect{Teaching experience}
\entry%
{01/2020 -- 04/2020}
{Graduate Teaching Assistant}
{\href{https://uva.nl/}{Universiteit van Amsterdam}}
{
    Assisting with the master level courses \textit{Information Retrieval} and \textit{Fairness, Accountability, Confidentiality and Transparency in AI}.
    Teaching tutorial sessions, correcting course work and support students in finishing scientific work and writing.
}
{}

\entry%
{10/2015 -- 02/2016}
{Teaching Assistant}
{\href{https://uni-heidelberg.de/en}{University Heidelberg}}
{
    Assisting with the Bachelor course \textit{Practical Computer Science}.
    Teaching in self-prepared weekly tutorial session.
}
{}

\cvsect*{Skills}
\begin{itemize}
    \item Excellent skills in machine learning engineering with Python: PyTorch, TensorFlow, Caffe, Pandas, SciPy, OpenCV, Scikit-Learn
    \item Excellent skills in using GNU/Linux systems: System administration, BASH, Perl, Git, Slurm
    \item Strong academic and technical writing skills as well as enthusiasm for writing useful tutorials (see blog)
    \item Strong skills in data visualization: pyplot, Dash (plotly), web technologies
    \item Engineering experience in working with: MATLAB, Java, C++, JavaScript\vspace{\baselineskip}
    \item \textit{Spoken languages}: German native, English fluent (TOEFL 112/120), Persian and Dutch beginner level
\end{itemize}

% \begin{minipage}[t]{.4\columnwidth}
%     \cvsect*{Languages}
%     \begin{itemize}[left=3.5em]
%         \item[\textbf{German}] native
%         \item[\textbf{English}] fluent\\(TOEFL 112/120)
%         % \item[\textbf{Persian}] \textit{beginner}
%         % \item[\textbf{Dutch}] \textit{beginner}
%     \end{itemize}
% \end{minipage}
% \begin{minipage}[t]{.6\columnwidth}
%     % \cvsect*{Academic references}
%     % \begin{itemize}
%     %     \item Prof Dr Efstratios Gavves (QUVA Lab)
%     %     \item Prof Dr Björn Ommer (Uni Heidelberg)
%     %     \item Dr Miguel Bautista Martin (Apple Inc)%:\\\href{mailto:mbautistamartin@apple.com}{mbautistamartin@apple.com}
%     %     \item Maximilian Ilse (AMLab)%:\\\href{mailto:M.Ilse@uva.nl}{M.Ilse@uva.nl}
%     % \end{itemize}
%     % \cvsect*{Personal interests}
%     % \begin{itemize}
%     %     \item Climbing
%     %     \item Mountaineering
%     %     \item Electronic music production
%     % \end{itemize}
% \end{minipage}

\end{multicols*}
\end{document}
