\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

\subsection{{Founding Engineer \hfill 2025 --- Present}}
\subtext{\href{https://www.peau.ai/}{peau.ai} \hfill Hamburg}
\begin{zitemize}
\item From 0 to MVP in 2 quarters.
\item Cross-platform Flutter-based app for personalized skincare, full-stack solution on Firebase and custom UI.
\item Custom Comupter vision models for skin analysis and LLM-based agents for recommendations and product discovery.
\item[] \texttt{Flutter{\|}Firebase{\|}Riverpod{\|}ML Kit{\|}Google Cloud}
\end{zitemize}

\subsection{{Founding Engineer \hfill 2024 --- Present}}
\subtext{\href{https://www.muno.ai/}{Muno} \hfill Hamburg}
\begin{zitemize}
\item Engineering the full-stack B2C platform for immune health, from backend blood RNA analysis pipelines to the customer-facing application.
\item[] \texttt{Python{\|}Bioinformatics{\|}ML Engineering}
\end{zitemize}

\subsection{{Founding Engineer \hfill 2023 --- Present}}
\subtext{\href{https://soilytix.com}{Soilytix} \hfill Hamburg}
\begin{zitemize}
\item From idea to revenue in 1 year. 
\item Architected and developed a data-driven platform for analyzing agricultural data, providing insights to farmers and agronomists.
\item Full-stack developed in Next.js with scalable backend, supporting world spanning data-sets. 
\item[] \texttt{Next.js{\|}TypeScript{\|}Prisma{\|}Mapbox{\|}Nivo{\|}Vercel}
\end{zitemize}

\subsection{{Software Architect Advisor \hfill 11/2024 --- Present}}
\subtext{\href{https://hummingbird-diagnostics.com/}{Hummingbird Diagnostics} \hfill Heidelberg}
\begin{zitemize}
\item Strategic consulting on ML architecture, MLOps, and software design for RNA sequencing analysis.
\item[] \texttt{MLOps{\|}Software Architecture{\|}ML Engineering}
\end{zitemize}

\subsection{{Machine learning scientist \hfill 11/2020 --- 11/2024}}
\subtext{\href{https://hummingbird-diagnostics.com/}{Hummingbird Diagnostics} \hfill Heidelberg}
\begin{zitemize}
\item Causal machine learning research on RNA-Seq. NGS and Nanopore data
\item Working with sequence embedding models and graph networks
\item In-house platform for data, feature, and result analysis and MLOps to enable for code-free ML analysis across large set of datasets and objectives.
\item[] \texttt{Python{\|}PyTorch{\|}sklearn{\|}Biostatistics}
\end{zitemize}

\subsection{{Research intern \hfill 11/2019 --- 06/2020}}
\subtext{\href{https://amlab.science.uva.nl/}{AMLab, University of Amsterdam} \hfill Amsterdam}
\begin{zitemize}
\item Intern at Max Welling's Machine Learning Lab at the University of Amsterdam.
\end{zitemize}

\subsection{{Machine learning engineer -- Intern \hfill 06/2019 --- 08/2019}}
\subtext{\href{https://bmwgroup.com}{BMW Group} \hfill Munich}
\begin{zitemize}
\item Building statistical models to analyze engine part quality and live fleet monitoring.
\item Building a production-ready data visualization app.
\item[] \texttt{Python{\|}PySpark{\|}Palantir Foundry{\|}Dash{\|}Agile development}
\end{zitemize}


\subsection{{Full-stack web developer \hfill 09/2017 --- 08/2018}}
\subtext{\href{https://buergerwerke.de/}{Bürgerwerke eG} \hfill Heidelberg}
\begin{zitemize}
\item Ground-up development of a team communication and organization web portal in Ruby on Rails.
\item[] \texttt{Rails{\|}Ruby{\|}Software Engineering}
\end{zitemize}


\end{document}